\chapter*{Hi!}
First of all, thanks for trying out Little Sound Dj!

A lot of effort has been put into making this program as powerful and fast-worked as possible. I hope you will enjoy.

If you don't have previous experience from similar ``tracker"-like music editors, the amount of new concepts may seem a bit overwhelming at first.  Try not to stress about it. Learn step by step, keep it fun and progress at your own pace. Within days, you should know enough about the program to make your own first songs.

About the structure of this manual: Chapter 1 helps you get started with the basics, while chapter 2 gives a high-level walkthrough of the entire program. These first two chapters should be enough to successfully use Little Sound Dj. Remaining chapters are advanced topics or reference material, and can be consumed at your own leisure, or skipped entirely if you so wish.

There is a lot of information that will not fit into a manual like this. For links to further resources I recommend checking out the user-maintained Wiki site at \url{https://wiki.littlesounddj.com} - it contains material like tutorials, tips and tricks, and hardware related DIY projects. Also, the Facebook group at \url{https://www.facebook.com/groups/LittleSoundDJ/} is useful for getting in touch
with other users.

If you have questions, ideas or bug reports related to Little Sound Dj or this manual, I would be delighted if you reach out by e-mailing \href{mailto:info@littlesounddj.com}{info@littlesounddj.com}.

Happy tracking!

\textit{/Johan}

